Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
More on `shouldThrow`
Use straightforward instead of trivial
Add comment for @kazu

BDD includes TDD, amongst other software development methodologies,
but with a terminology and mindset shifted towards
specification instead of testing.
In BDD, specifications can be used for
automatic testing.

\begin{quote}
    sol: maybe like so?  In addition to \emph{automating things}, this
    would also motivate \ref{sec:code-doc}, which is IMHO not
    motivated very well.

    BDD is meant to be an enjoyable experience for the developer.
    Compared to TDD it provides a much nicer syntax that
    makes tests very easy to read.  And like TDD it puts emphasis on
    test automation, to take work load from the shoulders of
    developers.
\end{quote}

BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

\begin{quote}
    BDD also includes other software development methods, such as
    automatic test discovery and continuous integration~\cite{ci}.

    sol: I removed this, and reverted the paragraph to it's previous
    version, because I think there were several issues.

    \begin{itemize}
        \item test discovery is not an aspect of BDD, only an emphasis
            on automating things is an aspect of BDD, so that
            \emph{testing is more fun} and \emph{things e.g. work with
            CI}.  This are two different things, but both justify automation.
            We only need this to justify our discussion of Cabal
            integration and automatic test discovery.  If we remove
            those, we do not need to state that ``automation is an important
            aspect of BDD''.  This may be a solution.
        \item @mkl your previous version stated, that BDD includes
            other things (ATDD!), but that we do not cover them.  This
            is very important.  And I think that meaning got lost with
            the change, hence the revert.
    \end{itemize}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
>>> length []
0
\end{verbatim}
\end{quote}

@@

@@

\noindent All combinators introduced in \ref{sec:code-doc} have been
implemented in the {\tt hspec-shouldbe} package\footnote{%
http://hackage.haskell.org/package/hspec-shouldbe};
and they will be incorporated into a future
release of Hspec.
The implementation is trivial, so we will not further discuss it.

>>>>

BDD includes TDD, amongst other software development methodologies,
but with a terminology and mindset shifted towards
specification instead of testing.
In BDD, specifications can be used for
automatic testing.
BDD is meant to be an enjoyable experience for the developer.
Compared to TDD it provides a much nicer syntax that
makes tests very easy to read.  And like TDD it puts emphasis on
test automation, to take work load from the shoulders of
developers.
BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

@@

\begin{quote}
    sol: @kazu should we make the Haddock examples in this section
    valid Haddock comments?
\end{quote}

\begin{quote}
\small
\begin{verbatim}
-- |
-- >>> length []
-- 0
\end{verbatim}
\end{quote}

@@

\noindent And it can be used with predicates from {\tt
System.IO.Error}, to require specific {\tt IOException}, e.g.  with
{\tt isPermissionError}:

\begin{quote}\small\begin{verbatim}
launchMissiles `shouldThrow` isPermissionError
\end{verbatim}\end{quote}

@@

\noindent All combinators introduced in \ref{sec:code-doc} have been
implemented in the {\tt hspec-shouldbe} package\footnote{%
http://hackage.haskell.org/package/hspec-shouldbe};
and they will be incorporated into a future
release of Hspec.
The implementation is straightforward, so we will not further discuss
it.
